full title

### 2020-10-27 paper/pldi21/abstract.tex
Adding citations on introduction.

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present the alloyed analysis, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
Our experimental results show that the alloyed analysis indeed speeds up the detection and reports bugs more precisely.
\end{abstract}

>>>>

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present the dynamic shortcut, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
Our experimental results show that the combined analysis indeed speeds up and produces more precise results.
\end{abstract}

### 2020-10-27 paper/pldi21/intro.tex
Adding citations on introduction.

\section{Introduction}\label{sec:intro}
JavaScript is the de facto programming language in web development and,
moreover, blossoming beyond the web.
JavaScript has dominated client-side scripting of the web for over a decade.
JavaScript takes the unique position as the universal language operating in both
the browser and on a server in the form of Node.js.
The client-side frameworks such as React, Vue.js, and Angular have accelerated
the universal use of JavaScript.
The cross-platform frameworks like React Native and Electron have spread
JavaScript to the new domains of mobile and desktop beyond the web.
This is only possible thanks to JavaScript's easy operation in development and
deployment with scripting language characteristics such as dynamic and
interpreted language features~\cite{weakly}.

However, such features make it difficult to support developer tools that require
statically reasoning about semantics of JavaScript programs such as call graph
construction, type checking, optimization, and bug detection.
For example, the combination of the JavaScript features: dynamically-computed
property name, prototype chain, and first-class function, makes call graph
construction challenging.
Even a minor precision loss at property name can cause reading all methods in
the object and its prototype chain, including hundreds of built-ins, that
results in useless analysis results.
In static analyses of Java, the benchmark results clearly show the trade-off
between precision and performance~\cite{}, a low degree of context sensitivity
shows a high performance but low precision.
In the case of JavaScript, the relationship between precision and performance is
more complex due to the spurious callee explosion.
Low precision tends to cause the large number of spurious callees, which
significantly degrades the performance~\cite{}.

For this reason, recent studies on JavaScript static analysis have proposed
techniques to improve analysis precision against this challenge.
Madsen et al.~\cite{} presented sophisticated abstract domains for strings.
Park and Ryu proposed high degrees of context sensitivity for loop~\cite{}.
Relations between object properties aid to analysis precision~\cite{}.
Demand-driven value refinement~\cite{} and lightweight variants of trace
partitioning~\cite{} showed promising results.

@@

Existing combined approaches derive three kinds of benefits of dynamic analysis.
Dynamic analysis can run on a highly-optimized JavaScript engine like V8, so
it boosts up analysis performance.
There is no precision loss coming from limitations of abstract domains and
sensitivities if the dynamic analysis terminates.
Dynamic analysis can pass by opaque codes that require extra handling for static
analysis.

However, the existing combined analyses are limited to maximize benefits of
dynamic analysis.
Staged analyses first collect particular information by dynamic analysis and
apply static analysis augmented with dynamic information.
Dynamic information can be argument length, object creation site, entire heap at
specific program points.
Once static analysis starts, it does not utilize more dynamic information.
The other design of combined analysis is divide whole program into two parts.
One for the dynamic analysis (framework code) and the other for the static analysis (user code).
The policy to divde a program is predefined and syntactic.
Each analysis always take on each part of code.

>>>>

\section{Introduction}\label{sec:intro}
JavaScript is the de facto programming language in web development and,
moreover, blossoming beyond the web.
JavaScript has dominated client-side scripting of the web for over a decade.
JavaScript takes the unique position as the universal language operating in both
the browser and on a server in the form of Node.js.
The client-side frameworks such as React, Vue.js, and Angular have accelerated
the universal use of JavaScript.
The cross-platform frameworks like React Native and Electron have spread
JavaScript to the new domains of mobile and desktop beyond the web.
This is only possible thanks to JavaScript's easy operation in development and
deployment with scripting language characteristics such as dynamic and
interpreted language features~\cite{weaklySPE}.

However, such features make it difficult to support developer tools that require
statically reasoning about semantics of JavaScript programs such as call graph
construction, type checking, optimization, and bug detection.
For example, the combination of the JavaScript features: dynamically-computed
property name, prototype chain, and first-class function, makes call graph
construction challenging.
Even a minor precision loss at property name can cause reading all methods in
the object and its prototype chain, including hundreds of built-ins, that
results in useless analysis results.
In static analyses of Java, the benchmark results clearly show the trade-off
between precision and performance~\cite{data-driven} \todo, a low degree of
context sensitivity shows a high performance but low precision.
In the case of JavaScript, the relationship between precision and performance is
more complex due to the spurious callee explosion.
Low precision tends to cause the large number of spurious callees, which
significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.

For this reason, recent studies on JavaScript static analysis have developed
to improve analysis precision against this challenge.
Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
Park et al. proposed high degrees of context sensitivity for loop~\cite{lsaECOOP, lsaSPE}.
Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.

@@

Existing combined approaches derive three kinds of benefits of dynamic analysis.
Dynamic analyses~\cite{jalangi, jalangi2, dlint} can run on a highly-optimized
JavaScript engine like V8, so it boosts up analysis performance.
There is no precision loss coming from limitations of abstract domains and
sensitivities if the dynamic analysis terminates~\cite{concerto}.
Dynamic analysis can pass by opaque codes that require extra handling for static
analysis~\cite{battles, sra}.

However, the existing combined analyses are limited to maximize benefits of
dynamic analysis.
Staged analyses first collect particular information by dynamic analysis and
apply static analysis augmented with dynamic information~\cite{staged, blendedJava, eha} \todo.
Dynamic information can be argument length, object creation site~\cite{blended}, entire heap at
specific program points~\cite{battles}.
Once static analysis starts, it does not utilize more dynamic information.
The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
One for the dynamic analysis (framework code) and the other for the static analysis (user code).
The policy to divde a program is predefined and syntactic.
Each analysis always take on each part of code.
